{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-09-23 ident_manu.tex
updating results with new fishtank mod

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Aug 30 15:34:01 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption{Sensitivity of \ac{do} to perturbations of indivividual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \ac{do} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}} 

@@

@@

\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}\tabularnewline

@@

{\bfseries Optics}&&&\tabularnewline
~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$6.27\times 10^{-4}$\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$3.22\times 10^{-4}$\tabularnewline
~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$5.35\times 10^{-6}$\tabularnewline

@@

{\bfseries Temperature}&&&\tabularnewline
~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)}&$22$&$1.8\times 10^{-4}$\tabularnewline

@@

{\bfseries Phytoplankton}&&&\tabularnewline
~~phytoplankton carbon/cell&\textit{Qc}&$1.35\times 10^{-6}$&$0.71$\tabularnewline
~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$8.42\times 10^{-17}$&$0.03$\tabularnewline
~~mortality coefficient&\textit{mA}&$0.1$&$0.03$\tabularnewline
~~N-uptake rate measured at umax&\textit{vmaxN}&$4.1\times 10^{-8}$&$0.03$\tabularnewline
~~coefficient for non-limiting nutrient&\textit{aN}&$1$&$0.01$\tabularnewline
~~phytoplankton basal respiration coefficient&\textit{respb}&$0.02$&$0.01$\tabularnewline
~~half-saturation constant for P&\textit{Kp}&$2.86$&$0.01$\tabularnewline
~~minimum N cell-quota&\textit{QminN}&$6.08\times 10^{-9}$&$7.44\times 10^{-3}$\tabularnewline
~~maximum growth rate&\textit{umax}&$0.41$&$5.34\times 10^{-3}$\tabularnewline
~~half-saturation constant for N&\textit{Kn}&$4.51$&$1.56\times 10^{-3}$\tabularnewline
~~P-uptake rate measured at umax&\textit{vmaxP}&$2.68\times 10^{-8}$&$1.3\times 10^{-3}$\tabularnewline
~~minimum P cell-quota&\textit{QminP}&$6.19\times 10^{-10}$&$1.59\times 10^{-4}$\tabularnewline
~~phytoplankton growth respiration coefficient&\textit{respg}&$0.1$&$7.63\times 10^{-5}$\tabularnewline

@@

{\bfseries Zooplankton}&&&\tabularnewline
~~zooplankton carbon/individual&\textit{ZQc}&$3.13\times 10^{-4}$&$4.51\times 10^{-3}$\tabularnewline
~~zooplankton nitrogen/individual&\textit{ZQn}&$6.95\times 10^{-5}$&$1.97\times 10^{-3}$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$&$1.47\times 10^{-4}$\tabularnewline
~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$7.2\times 10^{-4}$&$4.61\times 10^{-5}$\tabularnewline
~~zooplankton phosphorus/individual&\textit{ZQp}&$3.77\times 10^{-6}$&$2.89\times 10^{-5}$\tabularnewline

@@

{\bfseries Organic Matter}&&&\tabularnewline
~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$0.05$\tabularnewline
~~turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$0.01$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$7.53\times 10^{-3}$\tabularnewline
~~half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$6.49\times 10^{-3}$\tabularnewline
~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$6.36\times 10^{-3}$\tabularnewline
~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$8\times 10^{-4}$\tabularnewline
~~NH4 rate constant for nitrification&\textit{KNH4}&$1$&$2.9\times 10^{-4}$\tabularnewline
~~maximum rate of nitrification per day&\textit{nitmax}&$0.52$&$2.44\times 10^{-4}$\tabularnewline

@@

~~\footnotesize{\textit{astar490}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{astar490}}&$2$&$8.54$&$10.83$&-&-&-&$9.19$&$7.33$&-\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$2$&-&-&$3.86$&$1.43$&-&-&-&$3.63$\tabularnewline
~~\footnotesize{\textit{astarOMZ}}&$3$&-&$13.7$&$3.93$&$3.78$&-&$13.31$&$13.12$&$3.73$\tabularnewline

@@

~~\footnotesize{\textit{KG1}}&$1$&-&-&-&-&-&$1$&-&$1$\tabularnewline

@@

~~\footnotesize{\textit{KNH4}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$1$&-&-&$1$&-&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{KG1}}&$2$&-&$3.42$&$1.12$&$1.43$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$6.03$\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.9$&$1.73$&-\tabularnewline
~~\footnotesize{\textit{nitmax}}&$2$&$14.51$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$3$&-&-&$5.31$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$3$&$14.51$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KO2}}&$3$&-&-&-&$6.37$&-&$6.17$&$4.98$&-\tabularnewline

@@

~~\footnotesize{\textit{alpha}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$1$&-&-&$1$&$1$&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{QminP}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
~~\footnotesize{\textit{alpha}}&$2$&-&-&$1.66$&$1.36$&$4.98$&-&-&-\tabularnewline
~~\footnotesize{\textit{mA}}&$2$&-&-&-&-&-&-&-&$1.24$\tabularnewline
~~\footnotesize{\textit{umax}}&$2$&$8.51$&$4.64$&-&-&-&$6.1$&$5.36$&-\tabularnewline
~~\footnotesize{\textit{alpha}}&$3$&-&-&-&-&-&-&-&$4.73$\tabularnewline
~~\footnotesize{\textit{mA}}&$3$&$9.18$&$5.26$&$7.56$&$2.7$&-&$7.13$&$6.72$&-\tabularnewline
~~\footnotesize{\textit{respb}}&$4$&$13.74$&$9.62$&-&-&-&$13.32$&$14.3$&-\tabularnewline
~~\footnotesize{\textit{vmaxP}}&$4$&-&-&-&-&-&-&-&$6.18$\tabularnewline
~~\footnotesize{\textit{Qc}}&$5$&-&$13.06$&-&-&-&$13.35$&$14.39$&-\tabularnewline

@@

~~\footnotesize{\textit{ZQc}}&$1$&-&$1$&$1$&$1$&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{ZQn}}&$1$&$1$&-&-&-&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{ZQp}}&$1$&-&-&-&-&-&-&-&$1$\tabularnewline
~~\footnotesize{\textit{Zm}}&$2$&-&-&-&-&-&$2.76$&-&-\tabularnewline
~~\footnotesize{\textit{Zrespb}}&$2$&-&$5.46$&-&$5.88$&-&-&-&$1.66$\tabularnewline
~~\footnotesize{\textit{Zm}}&$3$&-&$14.16$&-&-&-&-&-&$4.21$\tabularnewline
~~\footnotesize{\textit{ZQp}}&$3$&-&-&-&-&-&$2.76$&-&-\tabularnewline
~~\footnotesize{\textit{ZQc}}&$4$&-&-&-&-&-&-&-&$5.23$\tabularnewline
~~\footnotesize{\textit{ZQp}}&$4$&-&$14.2$&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Zrespb}}&$4$&-&-&-&-&-&$12.49$&-&-\tabularnewline
~~\footnotesize{\textit{ZQn}}&$5$&-&-&-&-&-&$13.59$&-&-\tabularnewline

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\footnotesize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{Ammonium}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$8.51$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$9.18$\tabularnewline
~~4&\footnotesize{\textit{KNH4}}&$1$\textsuperscript{OM}&$11.35$\tabularnewline
\hline
{Chlorophyll}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$4.64$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$5.26$\tabularnewline
~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$9.62$\tabularnewline
~~5&\footnotesize{\textit{Tref(nospA+nospZ)}}&$1$\textsuperscript{T}&$12.93$\tabularnewline
\hline
{Dissolved Oxygen}&&&\tabularnewline
~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{Irradiance}&&&\tabularnewline
~~1&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$1$\tabularnewline
~~2&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1.15$\tabularnewline
~~3&\footnotesize{\textit{alpha}}&$2$\textsuperscript{P}&$2.5$\tabularnewline
~~4&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$2.92$\tabularnewline
\hline
{Nitrate}&&&\tabularnewline
~~1&\footnotesize{\textit{Qc}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{OM1}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$6.1$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$7.13$\tabularnewline
~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$13.32$\tabularnewline
~~5&\footnotesize{\textit{Qc}}&$5$\textsuperscript{P}&$13.35$\tabularnewline
\hline
{OM2}&&&\tabularnewline
~~1&\footnotesize{\textit{alpha}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$5.36$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$3$\textsuperscript{P}&$6.72$\tabularnewline
~~4&\footnotesize{\textit{respb}}&$4$\textsuperscript{P}&$14.3$\tabularnewline
~~5&\footnotesize{\textit{KG2}}&$1$\textsuperscript{OM}&$14.9$\tabularnewline
\hline
{Phosphate}&&&\tabularnewline
~~1&\footnotesize{\textit{QminP}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$1.24$\tabularnewline
~~3&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.73$\tabularnewline
~~4&\footnotesize{\textit{vmaxP}}&$4$\textsuperscript{P}&$6.18$\tabularnewline
~~5&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.17$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

{\bfseries Optics}&&&\tabularnewline
~~Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$2.71\times 10^{-3}$\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$2.41\times 10^{-3}$\tabularnewline

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Sep 6 12:52:12 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\caption{Sensitivity of \ac{do} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \ac{do} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}} 

@@

\begin{tabular}{lll}

@@

\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}\tabularnewline

@@

{\bfseries Optics}&&\tabularnewline
~~Chla specific absorption at 490 nm&\textit{astar490}&$7.41\times 10^{-4}$\tabularnewline
~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.91\times 10^{-5}$\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.34\times 10^{-5}$\tabularnewline

@@

{\bfseries Temperature}&&\tabularnewline
~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline

@@

{\bfseries Phytoplankton}&&\tabularnewline
~~maximum growth rate&\textit{umax}&$0.06$\tabularnewline
~~mortality coefficient&\textit{mA}&$0.02$\tabularnewline
~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.02$\tabularnewline
~~edibility vector for Z1&\textit{ediblevector(Z1)}&$0.02$\tabularnewline
~~phytoplankton carbon/cell&\textit{Qc}&$0.01$\tabularnewline
~~phytoplankton growth respiration coefficient&\textit{respg}&$8.28\times 10^{-3}$\tabularnewline
~~N-uptake rate measured at umax&\textit{vmaxN}&$8.15\times 10^{-3}$\tabularnewline
~~phytoplankton basal respiration coefficient&\textit{respb}&$6.93\times 10^{-3}$\tabularnewline
~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.41\times 10^{-3}$\tabularnewline
~~minimum N cell-quota&\textit{QminN}&$4.25\times 10^{-3}$\tabularnewline
~~coefficient for non-limiting nutrient&\textit{aN}&$4.2\times 10^{-3}$\tabularnewline
~~P-uptake rate measured at umax&\textit{vmaxP}&$4.19\times 10^{-3}$\tabularnewline
~~phytoplankton volume/cell&\textit{volcell}&$4.05\times 10^{-3}$\tabularnewline
~~half-saturation constant for P&\textit{Kp}&$2.9\times 10^{-3}$\tabularnewline
~~half-saturation constant for N&\textit{Kn}&$3.03\times 10^{-4}$\tabularnewline
~~minimum P cell-quota&\textit{QminP}&$1.4\times 10^{-7}$\tabularnewline

@@

{\bfseries Zooplankton}&&\tabularnewline
~~half saturation coefficient for grazing&\textit{ZKa}&$0.05$\tabularnewline
~~zooplankton nitrogen/individual&\textit{ZQn}&$0.02$\tabularnewline
~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.02$\tabularnewline
~~maximum growth rate of zooplankton&\textit{Zumax}&$0.02$\tabularnewline
~~assimilation efficiency as a fraction of ingestion&\textit{Zeffic}&$0.01$\tabularnewline
~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.58\times 10^{-3}$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.19\times 10^{-3}$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.89\times 10^{-3}$\tabularnewline
~~zooplankton carbon/individual&\textit{ZQc}&$9.48\times 10^{-5}$\tabularnewline
~~zooplankton phosphorus/individual&\textit{ZQp}&$3.63\times 10^{-5}$\tabularnewline

@@

{\bfseries Organic Matter}&&\tabularnewline
~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.1\times 10^{-3}$\tabularnewline
~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.59\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.11\times 10^{-3}$\tabularnewline
~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.95\times 10^{-3}$\tabularnewline
~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.68\times 10^{-4}$\tabularnewline
~~maximum rate of nitrification per day&\textit{nitmax}&$4.91\times 10^{-4}$\tabularnewline
~~NH4 rate constant for nitrification&\textit{KNH4}&$4.12\times 10^{-4}$\tabularnewline
~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.93\times 10^{-4}$\tabularnewline

@@

~~\footnotesize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$2$&$7.26$&$5.4$&-&$5.35$&-&$7.72$&$7.91$&-\tabularnewline
~~\footnotesize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.81$\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$3$&-&-&$3.73$&-&-&-&-&$9.65$\tabularnewline
~~\footnotesize{\textit{astarOMZ}}&$3$&$7.5$&$5.51$&-&$6.01$&-&$7.88$&$7.91$&-\tabularnewline

@@

~~\footnotesize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline

@@

~~\footnotesize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$13.44$\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.4$&-\tabularnewline
~~\footnotesize{\textit{KNH4}}&$2$&$4.04$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNO3}}&$2$&-&-&-&-&$9.1$&-&-&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$2$&-&-&$1.06$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG1}}&$3$&$4.1$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$3$&-&-&$6.01$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.78$\tabularnewline
~~\footnotesize{\textit{KO2}}&$3$&-&-&-&-&-&$14.25$&$12.35$&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$3$&-&$1.28$&-&$1.99$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$4$&-&-&-&$11.17$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$4$&-&-&$6.08$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.5$\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$4$&$4.29$&-&-&-&-&$14.34$&$13.61$&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$5$&$4.41$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KO2}}&$5$&-&-&$8.44$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{nitmax}}&$6$&-&-&$10.12$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNH4}}&$7$&-&-&$10.17$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNO3}}&$8$&-&-&$13.94$&-&-&-&-&-\tabularnewline

@@

~~\footnotesize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\footnotesize{\textit{ediblevector(Z1)}}&$2$&$1.13$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{mA}}&$2$&-&-&$1.16$&$1.28$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$2$&-&-&-&-&$3.38$&-&-&-\tabularnewline
~~\footnotesize{\textit{umax}}&$2$&-&$1.09$&-&-&-&$1.18$&$1.18$&-\tabularnewline
~~\footnotesize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$2.75$\tabularnewline
~~\footnotesize{\textit{alpha}}&$3$&-&-&$1.43$&$1.98$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{ediblevector(Z1)}}&$3$&-&$2.14$&-&-&-&$3.22$&$2.87$&-\tabularnewline
~~\footnotesize{\textit{umax}}&$3$&$1.23$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{alpha}}&$4$&$1.64$&$4.3$&-&-&-&-&$7.17$&-\tabularnewline
~~\footnotesize{\textit{ediblevector(Z1)}}&$4$&-&-&$1.83$&$3.15$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$4$&-&-&-&-&-&$5.2$&-&-\tabularnewline
~~\footnotesize{\textit{alpha}}&$5$&-&-&-&-&-&$9.72$&-&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$5$&-&-&$3.18$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{vmaxN}}&$5$&$8$&$14.42$&-&-&-&-&$14.48$&-\tabularnewline
~~\footnotesize{\textit{Athresh}}&$6$&$8.32$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{respg}}&$6$&-&$14.56$&$3.65$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{vmaxN}}&$7$&-&-&$4$&-&-&-&-&-\tabularnewline

@@

~~\footnotesize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\footnotesize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{ZKa}}&$2$&-&$3.48$&-&-&-&$5.38$&$4.15$&-\tabularnewline
~~\footnotesize{\textit{ZQn}}&$2$&-&-&$2.38$&$3.84$&$5.97$&-&-&$4.1$\tabularnewline
~~\footnotesize{\textit{Zm}}&$3$&-&-&$2.74$&-&-&-&-&$11.52$\tabularnewline
~~\footnotesize{\textit{Zumax}}&$3$&-&-&-&$5.94$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Zm}}&$4$&-&-&-&$6.9$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Zumax}}&$4$&-&-&$3.59$&-&-&-&-&-\tabularnewline

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
{Ammonium}&&&\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline
{Chlorophyll}&&&\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.1$\tabularnewline
{Dissolved Oxygen}&&&\tabularnewline
~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.27$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$2.37$\tabularnewline
~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.41$\tabularnewline
~~5&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.54$\tabularnewline
~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.9$\tabularnewline
~~7&\footnotesize{\textit{Zm}}&$3$\textsuperscript{Z}&$4.92$\tabularnewline
~~8&\footnotesize{\textit{Zumax}}&$4$\textsuperscript{Z}&$4.94$\tabularnewline
{Irradiance}&&&\tabularnewline
~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$5.03$\tabularnewline
~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.98$\tabularnewline
~~4&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$8.27$\tabularnewline
~~5&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$10.08$\tabularnewline
~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$10.09$\tabularnewline
~~7&\footnotesize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.83$\tabularnewline
{Nitrate}&&&\tabularnewline
~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$4.79$\tabularnewline
~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$6.88$\tabularnewline
{OM1}&&&\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$1.18$\tabularnewline
~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$3.18$\tabularnewline
~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.5$\tabularnewline
{OM2}&&&\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.74$\tabularnewline
~~4&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.86$\tabularnewline
~~5&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$5.44$\tabularnewline
{Phosphate}&&&\tabularnewline
~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$4.9$\tabularnewline
~~3&\footnotesize{\textit{vmaxP}}&$2$\textsuperscript{P}&$6.84$\tabularnewline
~~4&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$14.13$\tabularnewline

@@

{\bfseries Optics}&&\tabularnewline
~~Chla specific absorption at 490 nm&\textit{astar490}&$0.02$\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$1.46\times 10^{-3}$\tabularnewline
